Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2024-11-17 analysis/Stud1_a.qmd
make table1 more reproducible
@AnafNeves  :
- just noticed the sample size for df5 and df7c that we had written vs. the recomputed doesn't match, not sure if  that's expected
- The mean age is probably wrong too

>>>>

```{r}
#| output: false
#| warning: false

library(gt)

# APA style ####
gt_apastyle <- function(gt_table, font.size=12) {
  gt_table  |> 
    gt::opt_table_lines(extent = "none") %>%
    gt::tab_options(
      heading.border.bottom.width = 2,
      heading.border.bottom.color = "black",
      heading.border.bottom.style = "solid",
      table.border.top.color = "black",
      table.border.top.style = "solid",
      table.border.top.width = 2,  
      table_body.hlines.color = "white",
      table_body.border.top.color = "black",
      table_body.border.top.style = "solid",
      table_body.border.top.width = 2,
      heading.title.font.size = font.size,
      table.font.size = font.size,
      heading.subtitle.font.size = font.size,
      table_body.border.bottom.color = "black",
      table_body.border.bottom.width = 2,
      table_body.border.bottom.style = "solid",
      column_labels.border.bottom.color = "black",
      column_labels.border.bottom.style = "solid",
      column_labels.border.bottom.width = 1
    ) |> 
      gt::opt_table_font(font = "times")
}

make_age <- function(age) {
  age <- as.numeric(age)

  mean(age, na.rm = TRUE) |> 
    insight::format_value(digits=1) |> 
    paste0(" ± ", 
           insight::format_value(sd(age, na.rm = TRUE), digits=1)) 
}

# Create the dataframe
table <- data.frame(
  Sample = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Total'),
  Subsample = c('', 'Sample 1', 'Sample 2', '', '', '', '', '', '', 'Sample 1', 'Sample 2', 'Sample 3', '', 'Sample 1', 'Sample 2', '', '', '', ''),   
  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', ''),
  N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), 96, nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10a), nrow(df10b), 31317),
  Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "TODO*", "TODO*", make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10a$Age), make_age(df10b$Age), 49.5),
  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76', '17 - 93'),
  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', NA, '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '71.5%'),
  Availability= c('', '', 'https://osf.io/3m5nh', 'https://osf.io/5x9sg', 'https://osf.io/j6ef3', 'https://osf.io/ms354', 'https://osf.io/mp3cy', 'https://osf.io/xwz6g', '', '', 'https://osf.io/3f2h6', '','','', 'https://osf.io/3eztd', 'https://osf.io/7p9u5', 'https://github.com/RealityBending/IllusionGameReliability', 'https://github.com/DominiqueMakowski/PHQ4R', '')
)

table_apa <- table |> 
  gt() |>
  cols_align(align = c("right"), columns = "Age") |> 
  cols_label(Age = "Age (Mean  ± SD)", Female_Percentage = "Female %") |> 
  tab_footnote("* Information copied from the sample description rather than recomputed.") |> 
  gt_apastyle()

table_apa
gtsave(table_apa, "figures/table1.tex")
```

### 2024-11-17 paper/1_Initial/manuscript.qmd
make table1 more reproducible
@AnafNeves  :
- just noticed the sample size for df5 and df7c that we had written vs. the recomputed doesn't match, not sure if  that's expected
- The mean age is probably wrong too

---
title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates"
shorttitle: "IAS Factor structure and correlates"
author:
  - name: Magdalena Pfaff
    corresponding: true
    orcid: 0009-0006-2386-7936
    # roles: 
      # - Project administration
      # - Data curation
      # - Formal Analysis
      # - Investigation
      # - Visualization
      # - Writing – original draft
      # - Writing – review & editing
    affiliations:
      - id: id1
        name: "University of Sussex"
        department: School of Psychology
        # address: 1234 Capital St.
        # city: New York
        # region: NY
        # country: USA
        # postal-code: 12084-1234
# author-note:
#   status-changes: 
#     affiliation-change: null
#     deceased: null
#   disclosures:
#     study-registration: null
#     data-sharing: null
#     related-report: null
#     conflict-of-interest: null
#     financial-support: null
#     gratitude: null
#     authorship-agreements: null
    #   # - Project administration
    #   # - Data curation
    #   # - Formal Analysis
    #   # - Investigation
    #   # - Visualization
    #   # - Writing – original draft
    #   # - Writing – review & editing
    # Roles are optional. 
    # conceptualization, data curation, formal Analysis, funding acquisition, investigation, 
    # methodology, project administration, resources, software, supervision, validation, 
    # visualization, writing, editing
    #   - Conceptualization
    #   - Data curation
    #   - formal Analysis
    #   - Funding acquisition
    #   - Investigation
    #   - Methodology
    #   - Project administration
    #   - Resources
    #   - Software
    #   - Supervision
    #   - Validation
    #   - Visualization
    #   - Writing – original draft
    #   - Writing – review & editing
  - name: Ana Neves
    orcid: 0009-0006-0020-7599
    # roles:
    affiliations:
      - ref: id1 
  - name: Dominique Makowski
    corresponding: true
    orcid: 0000-0001-5375-9967
    email: D.Makowski@sussex.ac.uk
    url: https://realitybending.github.io/
    # Select from the CRediT: Contributor Roles Taxonomy https://credit.niso.org/
    # roles:
    affiliations:
      - ref: id1 
keywords: []
floatsintext: true
numbered-lines: true
bibliography: bibliography.bib
suppress-title-page: false
mask: false
# Language options. See https://quarto.org/docs/authoring/language.html
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  title-block-author-note: "Author Note"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
  references-meta-analysis:
format:
  apaquarto-docx: default
  apaquarto-html: default
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
editor: 
  markdown: 
    wrap: sentence
editor_options: 
  chunk_output_type: console
---

@@

```{r}
#| warning: false
#| label: tbl-samples
#| tbl-cap: "Blabla caption fds Samples demographics"
# #| apa-note: "Some note bedlow the table"

table <- data.frame(
  Studies = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', '***Total***'),
  Samples = c('', 'Sample 1', 'Sample 2', '', '', '', '', '', '', 'Sample 1', 'Sample 2', 'Sample 3', '', 'Sample 1', 'Sample 2', '', '', '', ''),   
  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', ''),
  N = c('', 451, 375, 814, 515, 802, 96, 619,'', 522, 1993, 802,'', 1166, 500, 21843, 485, 251, "\\textbf{31317}"),
  Age = c('', "25.8 ± 8.4 [18-69]", 35.3, 24.9, 30.7, 36.58, 28.78, 43.9,'', 23.4, 32.0, 27.3,'', 32.5, 37.4, 56.5, 30.1, 37.5, 49.5),
  SD = c('', 8.4, 16.9, 5.3, 10.5, 12.41, 27.5, 14.5,'',  6.7, 12.6, 9.3, '', 8.4, 7.4, 14.4, 10.1, 13.2, 13.2),
  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76', '17 - 93'),
  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', NA, '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '71.5%'),
  Link= c('', '', 'https://osf.io/3m5nh', 'https://osf.io/5x9sg', 'https://osf.io/j6ef3', 'https://osf.io/ms354', 'https://osf.io/mp3cy', 'https://osf.io/xwz6g', '', '', 'https://osf.io/3f2h6', '','','', 'https://osf.io/3eztd', 'https://osf.io/7p9u5', 'In preparation **', 'In preparation **', '')
)

knitr::kable(table, format = "latex", booktabs = TRUE, longtable = TRUE, col.names = stringr::str_replace(names(table), "Female_Percentage", "Female %")) |> 
  kableExtra::kable_styling(font_size = 7)
```

Our search focused on studies citing the original IAS validation paper [@murphy2019], identifying 136 papers (as of **XX/XX/2024**).
To qualify for inclusion, papers needed to (1) provide accessible data in open-access, (2) employ the IAS as a measure, and (3) report individual IAS items scores.
A total of 9 studies was included.
Additionally, we added datasets of two unpublished (but already open-access) studies from our lab.
**See @tbl-samples** for a summary of the samples demographics.

<!-- **Table 1.** Samples demographics -->

<!-- | Samples                  |          | Language of Items|  Sample Size | Mean age | SD      | Range   | Female % | Available at           | -->

<!-- |---------|---------|---------|---------|---------|---------|---------|---------|---------| -->

<!-- | Murphy et al., (2020)    |          |             |          |         |         |          |                        | -->

<!-- |                          | Sample 1 | English     |451         | 25.8     | 8.4     | 18-69   | 69.4%    |                        | -->

<!-- |                          | Sample 2 | English     | 375         | 35.3     | 16.9    | 18-91   | 70.1%    | <https://osf.io/3m5nh> | -->

<!-- | Gaggero et al., (2021)   |          | English and Italian   | 814         | 24.9     | 5.3     | 18-58   | 60.3%    | <https://osf.io/5x9sg> | -->

<!-- | Campos et al., (2022)    |          | Portuguese  | 515         | 30.7     | 10.5    | 18-72   | 59.6%    | <https://osf.io/j6ef3> | -->

<!-- | Todd et al., (2022)      |          | English     | 802         | 36.58\*  | 12.41\* | 18-92\* | NA       | <https://osf.io/ms354> | -->

<!-- | Arslanova et al., (2022) |          | English     | 96          | 28.78    | 27.5    | 18-73   | 46.8%    | <https://osf.io/mp3cy> | -->

<!-- | Brand et al., (2022)     |          | German      | 619         | 43.9     | 14.5    | 18-78   | 78.7%    | <https://osf.io/xwz6g> | -->

<!-- | Brand et al., (2023)     |          |             |             |          |         |         |          |                        | -->

<!-- |                          | Sample 1 | German      | 522         | 23.4     | 6.7     | 18-79   | 79.5%    |                        | -->

<!-- |                          | Sample 2 | German      |1993        | 32.0     | 12.6    | 16-81   | 77.7%    | <https://osf.io/3f2h6> | -->

<!-- |                          | Sample 3 | German      | 802         | 27.3     | 9.3     | 18-72   | 68.9%    |                        |instaiin -->

<!-- | Lin et al., (2023)       |          |             |             |          |         |         |          |                        | -->

<!-- |                          | Sample 1 | Chinese     | 1166        | 32.5     | 8.4     | 16-60   | 57.0%    |                        | -->

<!-- |                          | Sample 2 | Chinese     | 500         | 37.4     | 7.4     | 20-60   | 56.2%    | <https://osf.io/3eztd> | -->

<!-- | VonMohr et al., (2023)   |          | English     | 21843       | 56.5     | 14.4    | 18-93   | 73.2%    | <https://osf.io/7p9u5> | -->

<!-- | Makowski et al., (2023a) |          | English     | 485         | 30.1     | 10.1    | 18-73   | 50.3%    | In preparation \*\*    | -->

<!-- | Makowski et al., (2023b) |          | English     |251         | 37.5     | 13.2    | 17-76   | 53.0%    | In preparation \*\*    | -->

<!-- | Total                    |          |             |31317       | 49.5     | 13.2    | 17 - 93 | 71.5%    | | -->

@@

<!-- **TODO: add row for Total N, average age etc.** -->

>>>>

---
title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates"
shorttitle: "IAS Meta-analysis"
author:
  - name: Ana Neves
    corresponding: true
    orcid: 0009-0006-0020-7599
    # roles: 
      # - Project administration
      # - Data curation
      # - Formal Analysis
      # - Investigation
      # - Visualization
      # - Writing – original draft
      # - Writing – review & editing
    affiliations:
      - id: id1
        name: "University of Sussex"
        department: School of Psychology
        # address: 1234 Capital St.
        # city: New York
        # region: NY
        # country: USA
        # postal-code: 12084-1234
# author-note:
#   status-changes: 
#     affiliation-change: null
#     deceased: null
#   disclosures:
#     study-registration: null
#     data-sharing: null
#     related-report: null
#     conflict-of-interest: null
#     financial-support: null
#     gratitude: null
#     authorship-agreements: null
    #   # - Project administration
    #   # - Data curation
    #   # - Formal Analysis
    #   # - Investigation
    #   # - Visualization
    #   # - Writing – original draft
    #   # - Writing – review & editing
    # Roles are optional. 
    # conceptualization, data curation, formal Analysis, funding acquisition, investigation, 
    # methodology, project administration, resources, software, supervision, validation, 
    # visualization, writing, editing
    #   - Conceptualization
    #   - Data curation
    #   - formal Analysis
    #   - Funding acquisition
    #   - Investigation
    #   - Methodology
    #   - Project administration
    #   - Resources
    #   - Software
    #   - Supervision
    #   - Validation
    #   - Visualization
    #   - Writing – original draft
    #   - Writing – review & editing
  - name: Magdalena Pfaff
    corresponding: true
    orcid: 0009-0006-2386-7936
    affiliations:
      - ref: id1 
  - name: Dominique Makowski
    corresponding: true
    orcid: 0000-0001-5375-9967
    email: D.Makowski@sussex.ac.uk
    url: https://realitybending.github.io/
    # Select from the CRediT: Contributor Roles Taxonomy https://credit.niso.org/
    # roles:
    affiliations:
      - ref: id1 
keywords: []
floatsintext: true
numbered-lines: true
bibliography: bibliography.bib
suppress-title-page: false
mask: false
# Language options. See https://quarto.org/docs/authoring/language.html
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  title-block-author-note: "Author Note"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
  references-meta-analysis:
format:
  apaquarto-docx: default
  apaquarto-html: default
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
editor: 
  markdown: 
    wrap: sentence
editor_options: 
  chunk_output_type: console
---

@@

Our search focused on studies citing the original IAS validation paper [@murphy2019], identifying 136 papers (as of **XX/XX/2024**).
To qualify for inclusion, papers needed to (1) provide accessible data in open-access, (2) employ the IAS as a measure, and (3) report individual IAS items scores.
A total of 9 studies was included.
Additionally, we added datasets of two unpublished (but already open-access) studies from our lab.
See @tbl-samples for a summary of the samples demographics.

```{r}
#| warning: false
#| label: tbl-samples
#| tbl-cap: "Blabla caption for Samples demographics"
# #| apa-note: "Some note bedlow the table"

```

\tiny 
\input{../../analysis/figures/table1.tex}
\normalsize

@@
